### 2010-03-04 docs/analysis/analysis.tex
restructuring
more analysis routine documentation

@@

\section{General Analysis Routines}

@@

\item {\tt faverage2d.f90}, {\tt faverage3d.f90}

  Laterally average each of the variables in a plotfile (separate
  routines exist for 2-d and 3-d).  This is written with MAESTRO
  plane-paralle geometry plotfiles in mind, and the averaging is done
  over the coordinate direction(s) perpendicular to gravity.

@@

\item {\tt fIDLdump.f90}

@@

>>>>

\section{The {\tt data\_processing} Routines}

@@

To compile any of the individual routines, edit the {\tt GNUmakefile}
add uncomment the line beginning with `{\tt programs +=}' containing
the routine you want to build.

\subsection{General Analysis Routines}

@@

\item {\tt faverage.f90}

  Laterally average each of the variables in a plotfile (works for
  both 2-d and 3-d).  This is written with MAESTRO
  plane-parallel geometry plotfiles in mind, and the averaging is done
  over the coordinate direction(s) perpendicular to gravity.

\item {\tt fboxinfo.f90}

  Print out some basic information about the number of boxes on each
  refinement level and (optionally) the bounds of each of the boxes.

@@

\item {\tt fIDLdump.f90}, {\tt fIDLdump3d.f90}

@@

\subsection{Data Processing Example}

A well-commented example processing routine is provided in {\tt
  data\_processing/tutorial} as {\tt fspeciesmass2d.f90}.  This
routine simply computes the total mass of a particular species on the
entire domain for a 2-d dataset.  It is written to understand a
multilevel (AMR) dataset, and only considers the finest-available data
at any physical location in the computational domain.

{\tt fspeciesmass2d.f90} should provide a good starting point for
writing a new analysis routine for BoxLib data.
